---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sepa

<!-- badges: start -->
[![R-CMD-check](https://github.com/simonmoulds/sepa/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/simonmoulds/sepa/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The sepa package provides access to environmental data collected by the Scottish Environment Protection Agency (SEPA). 

## Installation

You can install the development version of sepa from [GitHub](https://github.com/) with:

```{r}
devtools::install_github("simonmoulds/sepa")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(dplyr)
library(lubridate)
library(ggplot2)
library(sepa)
```

The steps required to download historical streamflow data are outlined below: 
```{r}
grps <- sepa_group_list()
q_grp <- grps |> filter(group_name %in% "StationsWithFlow") |> pull(group_id)
# List stations that measure flow
stns <- sepa_station_list(group_id = q_grp)
# Choose arbitrary station
stn_id <- stns$station_id[1]
available_ts <- sepa_timeseries_list(stn_id)
# Get the timeseries ID for daily mean flow
ts_id <- available_ts |> 
  filter(stationparameter_name == "Flow" & ts_name == "Day.Mean") |> 
  pull(ts_id)
# Retrieve data
ts <- sepa_timeseries_values(ts_id, start_date = Sys.Date() %m-% months(1), end_date = Sys.Date())
head(ts)
```

Once we have obtained the data we can plot the timeseries:

```{r, echo = FALSE}
p <- ggplot(data = ts, aes(x = Timestamp, y = Value)) + geom_line()
p
```